---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---
### Reproducable Research Assignment1

### the document builds up the answers to Questions in Assignment1 step by step


## Loading and preprocessing the data
```{r }
##Read the data
StepsData<-read.table("activity.csv",header=TRUE,sep=",")
##check the data
head(StepsData)
```

## What is mean total number of steps taken per day?
#####      1.Calculate the total number of steps taken per day
 
```{r echo=TRUE,warning=FALSE}
library(dplyr)
##consider the cases without NA
StepsData_noNA<-StepsData[complete.cases(StepsData),]
head(StepsData_noNA)

##Table the sum total steps taken per day
StepsDay_Sum<-aggregate(steps~date,StepsData_noNA,sum)
head(StepsDay_Sum)
```
 
   
      
#####      2.If you do not understand the difference between a histogram and a barplot, research the difference  between them. Make a histogram of the total number of steps taken each day
      
```{r echo=TRUE,warning=FALSE}
##Make a histogram of the total number of steps taken each day
hist(StepsDay_Sum$steps,xlab="No. of Steps /Date(Day)",ylab="count",col="light green",border="red",main="Histogram for Total Steps/day")
``` 
  
 #####      3.Calculate and report the mean and median of the total number of steps taken per day
      

```{r echo=TRUE,warning=FALSE}
##Report the mean and median of the Data
mean(StepsDay_Sum$steps)
median(StepsDay_Sum$steps)
```
##__________________________________________________________________________________


## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
